Adopting agile software development in the large organizations: A systematic literature review

### 2014-06-01 journal/article.tex
T: Piloting: Work in progress

What kind?

@@

Did it work?

Big bang + Piloting
[P11, P16, P18, P41]

@@

@@

>>>>

What kind?   Phony, real projects

@@

What was found?

Benefits?

What after?

@@

% Piloting

A logical first step in an agile transformation is to try out the new methods in
a pilot project. A large amount of the primary studies described how piloting
was used in the beginning of the transformation.

A piloting stage was seen as important for any transformation [P8, P21].

Organizations typically start wit a pilot, and go through a gradual
transformation [P11].

Even reports which presented a big bang adoption described that the main
transformation was preceeded by piloting [P11, P18, P41].

Pilots could refer to considerable size. In one case over 100 people
participated in 8 pilot projects [P8].

A structured initiation approach for agile projects was created based on the
pilots [P8].

As a result of a successful pilot management approved use of agile [P14].

@@

[P6]
* Who: Broad set of services
* Amount: 4 teams

[P7]
* Who: Identified teams
* Amount: Many teams
* Result: Promising changes were seen
* Particular: Those who sere not involved were not impressed

[P8]
* Why: A pilot is important in any transformation
* Who: Teams with varying characteristics, a particular selection process
* Kind: Piloting with real projects were seen as important, multi-team pilot projects
* Amount: 8 projects with 100 people
* Found: The startup activities were difficult
* Particular: There was a selection process to screen teams
* Particular: Many teams in one pilot project
* Benefit: Piloting revealed critical spots: Start up, coaching, product owner role
* Benefit: A structured initiation approach for agile projects was created based on the pilots

[P9]
* Who: Volunteer teams
* What: Optional pilot programs were recommended to d ifferent parts of the organization
* Amount: 4 projects
* Benefit: The pilot provided insights in deficiencies
* Benefit: The pilot demonstrated benefits: Breaking down silos
* Particular: Some teams were mandated to use agile based on the pilots

[P10]
* Why: Some people just decided to give the new method a go

[P11, P33]
* Why: Mangement wanted to see if a new method could be achieved and be maintained
* Amount: One team

[P14]
* When: The agile process had been defined
* Amount: 7 pilot projects, 4 months
* Found: The pilots were successful
* Benefit: Management approved agile

[P16]
* Particular: A specific pilot project was decided to be avoided, so that there
              would not be dissonances in the organization
* A large amount of people were sent to training, and then they just started using agile

[P18]
* Amount: 1 team
* Result: Management decided to go on with agile. Other teams started copying the approach
* Result: More pilots were initiated
* Amount: 20 teams, 3 months
* Result: Continue agile where it works, in other cases not
* Result: The pilots surfaced problems that had been ignored

[P21] (!)
* A pilot was not conducted
* It was a critical mistake to ignore piloting

[P22]
* Amount: 1 team
* Result: The pilot gave the final look for the team area, a Team Area concept was created

[P24]
* What: There was experimenting with Scrum
* Result: Good results, and it was decided to roll out the method in all loactions

[P29] (?)
* Why: The method was piloted first within the team in order to give it a soft landing
* What: Try the method without altering it too much
* What: Piloting seems to mean that the methodology is just tried non-full-heartedly
* What: The pilot project lasted long enough to face many of the problems that
        agile had in the environment in question

[P36]
* Amount: A project
* What: Agile was tried within the organization
* Result: The project was successful and management became convinced of benefits

[P38]
* Why: Management needed to show benefits of agile greatly
* Who: A project was selected particularly for the pilot
* Who: It was a project deemed to be plausible for a good end result
* Result: The pilot was successful
* Result: Business was pleased with the result
* Particular: People got false expectations based on the success of the pilot
